Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
Updated

        \caption{LGC with closure collection based on liveness.\label{algo:lgc-a}}
\end{algorithm}
Algorithm~\ref{algo:lgc-a}  describes  a  liveness-based  garbage  collection
scheme.    Starting  with the root set, each  live reference is
explored   using  $\mathit{  lgcCopy}$.    Copying  \CONS\   cells  is
simple---it  just involves  copying  the cell  itself and  recursively
copying the \CAR\ and  the \CDR\ fields.

Let   us  consider   determining  the   liveness  of   a   closure  at
runtime. Assume  that the closure  $(app~f~y)$ has a  reference from
the root  set variable $x$. If $x$  is live,  then we  know that the
cell $(app~f~y)$ has  to be copied. However, to find out  the
liveness of $y$, could find out the program point which triggered the
evaluation of $(app~f~y)$ and pick up the liveness of $y$ from this
program point. However, this is only possible if the activation record
of the function which created this closure is still on the activation
stack. This does not always happen since a function could pack a
closure in a \CONS\ cell and return the \CONS\ cell.

>>>>

        \caption{LGC with closure collection based on liveness.\label{algo:lgc-a}}
\end{algorithm}
Algorithm~\ref{algo:lgc-a}   describes    a   liveness-based   garbage
collection scheme.  Starting with the root set, each live reference is
explored  using   $\mathit{  lgcCopy}$.    Copying  \CONS\   cells  is
simple---it  just involves  copying  the cell  itself and  recursively
copying the  \CAR\ and the  \CDR\ fields.   On the other  hand copying
closures  requires  determining  the  liveness  of  its  arguments  at
run-time.

Let   us  consider   determining  the   liveness  of   a   closure  at
runtime. Consider  a closure  $(app~f~y)$ has a  reference from
the root  set variable $x$. If $x$  is live,  then we  know that the
cell $(app~f~y)$ has  to be copied. To find out  the
liveness of $y$, we need the program point which triggered the
evaluation of $(app~f~y)$ and pick up the liveness of $y$ from this
program point. However, this is only possible if the activation record
of the function which created this closure is still on the activation
stack. This does not always happen since a function could pack a
closure in a \CONS\ cell and return the \CONS\ cell.
